%************************************************
\chapter{Methodology}\label{ch:workflow}

In this chapter we discuss the tools used for this project as well as the workflow followed in the development. 

Agile development is an iterative and incremental method. It focuses on delivering working software in short iterations which makes it a perfect approach to undertake this project considering its time limitations and goals.

The defined phases for this work are:
\begin{itemize}
	\item Modification of the existing open source simulation. The goal of the software currently available is not to simulate \textit{Angry Birds} levels but to allow the user play the game using previously generated. 
	\item Determine the different elements of the evolutionary algorithm, such as fitness, representation and operators. This requires a previous study of feasible options. 
	\item Selecting or developing a framework for the evolutionary algorithm. There are several frameworks available but not all of them will satisfy our requirements. 
	\item Experiments and results.
\end{itemize}

Those phases are not sequential as they overlap. Obviously, there is a logic order for them and therefore there was be a major focus on the first phase early in the development, moving this focus to the following part as the project progressed. 

The overlapping of the other three tasks is greater, providing a better environment for agile development. Each iteration expanded for about two weeks, in  which an increment was delivered. 

First increments consisted in modifications to the simulation and a study of different representations based on previous work on the same topic or related. After that, development started with integration of the simulation and the evolutionary program as well as a comparison of different frameworks. The framework and genetic operators were developed in parallel along with tests.

The increments also included experiments as they were based on hypotheses from previous results. 

The tools involved in the development of this project were:

\begin{itemize}
	\item Unity Engine (C\#), for the game adaptation.
	\item Python standard library, for the evolutionary algorithm.
	\item \LaTeX, for this document.
\end{itemize}

%************************************************

%*****************************************
%*****************************************
%*****************************************
%*****************************************
%*****************************************
